Dependent Object Types

### 2012-09-19 doc/fool/article.tex
expansion blurb
stub

@@

>>>>

The expansion judgement $\Gamma \ts T \expand_z {\seq {D}}$
``flattens'' all the declarations of a type: it relates a type $T$ to
a set of declarations that describe the type structurally. Expansion
is precise and unique, though it doesn't always
exist.

@@

\subsection{Glbs and Lubs}

In DOT, the glb of two types is their intersection and their lub,
their union. Recall the introductory example which was problematic in
Scala:
\begin{lstlisting}
  trait A { type T <: A }
  trait B { type T <: B }
\end{lstlisting}

We represent it as follows in DOT:
\begin{align*}
\mlnew p {&\Top \mlrefine p {\\
&\ \Ldecl {A_c} \Bot {\Top \refine z {\Ldecl T \Bot {z.A_c}}}\\
&\ \Ldecl {B_c} \Bot {\Top \refine z {\Ldecl T \Bot {z.B_c}}}\\
&}\ldefs{}}{}
\end{align*}

The glb is of $p.A_c$ and $p.B_c$ is $p.A_c \tand p.B_c$ by
definition.

What is the expansion of $p.A_c \tand p.B_c$? It is the set ${\Ldecl T
  \Bot {p.A_c \tand p.B_c}}$.
